% Chapter Template

\chapter{Introduction} % Main chapter title

\label{Chapter1} % Change 1 to a consecutive number; for referencing this chapter elsewhere, use \ref{Chapter1}

\section{Definition}
A lot of companies and individual developers are torn of which framework or library to choose for building client-side applications. ReactJS and Angular are the two most popular choices used for this purpose, and their comparison is one of the most popular topics in the tech community. In this thesis, it is aimed to compare these two technologies based on different metrics, such as popularity, performance, structure and many more. \par

\section{Research Goal}
The objectives of this thesis are to cite the main concepts of web applications and architectural design layers, to introduce the most popular front-end developing tools, ReactJS and Angular, and concluding with the evaluation of the analyzed frameworks and libraries based on a variety of metrics.

\section{Thesis's Structure}
This thesis is structured into 6 chapters. Chapter \ref{Chapter2} presents some basic concepts of web applications and introduces the web's architectural layers, what dynamic pages and Rest are, and how the data structure of an application is conducted. Chapter \ref{Chapter3} and \ref{Chapter4} describes in detail the structure and component model of ReactJS and Angular. Chapter \ref{Chapter5} contains the evaluation of the framework and library analyzed, with each evaluable aspect divided into sections. Chapter \ref{Chapter6} concludes this thesis and set future work to be done.