% Chapter Template

\chapter{Projects/Activities} % Main chapter title
%σύντομη περιγραφή όλων των δραστηριοτήτων που ανέλαβα

\label{Chapter3}

During my internship, I took part in quite a few projects that were mostly related to Beat Hotels product, either bugs resolved or entirely new features created, or Greek Marketing’s requirements. All of these projects will be analyzed in this chapter, expect of the ones of Chapter \ref{Chapter4} that will just mentioned so as to avoid repetition.

\section{Project 1: Price Estimator- Rides for Approval}

BeatHotels is a totally different product than Beat and a newly introduced one as described in the previous Chapters. For this reason, this new product is combined with a different driver app and a dashboard used from agents. Agents use the dashboard in order to control rides made through BeatHotels App and even start a ride or cancel one if it is needed. This new product does not have any price estimator for the rides made which means that a driver could theoretically add. By the term “price estimator”, we mean that 

\section{Project 2: Geo - Npm Package}


\section{Project 3: Statistics (analyzed in next Chapter)}

"Statistics" project is an external feature in Agent's dashboard that reveals total rides and Gross Merchandise Volume (GMV) gained from BeatHotel service. This project was separated in three main parts, the creation of stats npm package, customized statistics and general statistics, that will be described in detail in next Chapter. Generally, there were added charts in the BeatHotel's web application that present data based on different parameters chosen by Agents. In the chart, the given period's data are also compared with the previous week's or year's data and useful information are extracted for BeatHotel service.

\section{Project 4: Geofence in New Map}
Geofence in New Map- production (feature-deckGLMap)

\section{Project 5: Arc for accepted Drivers in Map}
Arc for accepted Drivers in Map- production (PR)

We want an arc to be added in "Live Map" Tab from the driving vehicle in the map to the pickup location. (12/06/19) (23/05 asana)

\section{Project 6: Babel Configuration for running code in both front-end and back-end}

(13/05/19)

\section{Project 7: Add StartTimestamp- endtimestamp and HQ}
Added to Completed Rides timestamps and link driver to HQ- production (PR)

In "Completed Rides Tab" on Beat Hotels Services - HQ we want to add  the ride ended time named "End Time" in the window which agents see more info about the ride. (6/05/19 asana)

In "Completed Rides Tab" on Beat Hotels Services - HQ we want to add the time of request named "Request Time" of the ride. (requesttimestamp on firebase) in the window which agents see more info about the ride.

In "Completed Rides Tab" on Beat Hotels Services - HQ we want agents by clicking on the Driver's Plates, his profile on HQ ((https://hq-gr.taxibeat.com/driver/edit/9351/) to be appeared.

\section{Project 8: Eliminate Errors in console and eslint errors}
Eliminate Errors in console and eslint errors (PR)

Remove all warnings from console (generated from ESLint) (22/05/19 asana)

\section{Project 9: Add button for unblocking dispatching status-production}
Add button for unblocking dispatching status-production (PR)


\section{Project 10: Landing page mpaineis-vgaineis}
Landing page for mpaineis-vgaineis.gr competition- production + responsive

\section{Project 11: Statistics in Dashboard - "Forecast"}
In Statics in Dashboard Tab, we want in the diagram to be completed for the rest hours of the day that we don't have yet data, from the rides and gmv of the previous week. (18/06)

\section{Project 12: Input location}
%, refactor Dispatch page and change modal to be responsive- branch feature-input-location_dispatch-driver

%Small brief

\section{Project 13: Zoom to hotel and driver}

We want when agents are searching for driver plates on "Live Map Tab" to be zoomed in this specific driver. (??)

We want in "Live Map" Tab, to be a filter like "Filter by Plates or Phone" where agents will be able to search a Hotel and the map zooms in the filtered Hotel.

%Θα ήθελα να σας ενημερώσω ότι πλέον μπορείτε στο Live Map, να αναζητήσετε ένα ξενοδοχείο και να κάνει zoom στο αντίστοιχο ξενοδοχείο πάνω στον χάρτη. Να σημειωθεί ότι πρέπει να συμπληρωθεί ακριβώς το ξενοδοχείο που επιθυμείτε εάν πρόκειται για ξενοδοχεία που περιλαμβάνουν την ίδια λέξη. (π.χ. εάν πληκτρολογήσετε την λέξη Divani, δεν θα κάνει zoom σε κάποιο ξενοδοχείο, θα πρέπει να πληκτρολογήσετε Divani Caravel, Divani Apollon, κτλ).

%Zoom in maps: Πλέον στο tab "Live Map", όταν αναζητάτε ένα όχημα βάσει Plates ή Phone, αυτόματα γίνεται zoom, στο οδηγό με αυτά τα στοιχεία. Εδώ να τονιστεί ότι για να γίνει zoom θα πρέπει τα στοιχεία Plates ή Phone να είναι μοναδικά για τον οδηγό εκείνη την στιγμή στον χάρτη. (Εάν δηλαδή μία στιγμή στον χάρτη υπάρχουν δύο οδηγοί που οι πινακίδες τους ξεκινάνε από 13 και πλητρολογήσετε το 13 στο search bar δεν θα γίνει zoom σε κάποιον οδηγό παρά μόνο εάν πληκρολογήσετε ολόκληρη την μοναδική πινακίδα του οδηγού).

\section{Project 14: Restructure Setting Component}

\section{Project 15: Get rid of old maps}

We want to get rid of old maps in completed rides and in approved rides and replace with the new maps. More specifically we have to get rid of the package "React MapboxGL"

%10 pages, 10 projects